---
title: "Sandbox"
author: "Kevin A. Ryan (JHUAPL)"
date: "Wednesday, September 16, 2015"
output: html_document
---
lines[[1]]<-"1 1"
lines[[2]]<-"-1"
```{r}
lines<-0
lines[[1]]<-"1 1"
lines[[2]]<-"-1"
line1 <- sapply(strsplit(lines[[1]], " "), as.numeric)
line2 <- sapply(strsplit(lines[[2]], " "), as.numeric)

x<-length(line1)-1
Betas<-line1[1:x]
Error<-line1[x+1]
Data<-line2
Y<-exp((sum(Data*Betas))+Error)
p<-Y/(1+Y)


n<-lines1[1]
k<-lines1[2]
k<-5

#even - n/2
#odd - 3n+1
x<-n

for (i in 1:k) {
     
if ((x%%2)==0) {x<-(x/2)}  
        else {x<-((3*x)+1)}
}

print(x)

```




```{r}
lines<-0
lines[[1]]<-"111 5"
lines1 <- sapply(strsplit(lines[[1]], " "), as.numeric)[,1]
n<-lines1[1]
k<-lines1[2]
k<-5

#even - n/2
#odd - 3n+1
x<-n

for (i in 1:k) {
     
if ((x%%2)==0) {x<-(x/2)}  
        else {x<-((3*x)+1)}
}

print(x)


```






```{r}
lines<- "I may opt for a top yam for Amy, May, and Tommy."

T <- "We promptly judged antique ivory buckles for the prize "
T <- strsplit(T, "")
T = sort(unique(tolower(unlist(T))))
T=gsub("[^[:alnum:]]","",T)[-1]
if(sum(T%in%letters)==26){T="pangram"}else{T="not pangram"}
write(as.character(T), stdout())

```


```{r}
```{r}
lines<-0
lines[[1]]<-"8 3"
lines1 <- sapply(strsplit(lines[[1]], " "), as.numeric)[,1]
M<-lines1[1]
N<-lines1[2]

output<-choose(M,N)
write(output, "")

#data=suppressWarnings(readLines(file("stdin")))
#data=strsplit(data,split=" ")
N=as.numeric(lines[[1]])
X=as.numeric(lines[[2]])


```



```{r}
lines<-0
lines[[1]]<-"1.5 2 -1 -2.5 3"
lines[[2]]<-"2 -1 2 .5"
lines

actual1 <- sapply(strsplit(lines[[1]], " "), as.numeric)[,1]


#data=suppressWarnings(readLines(file("stdin")))
#data=strsplit(data,split=" ")
N=as.numeric(lines[[1]])
X=as.numeric(lines[[2]])


```






 
Pangram
```{r}
# Enter your code here. Read input from STDIN. Print output to STDOUT
T <- "We promptly judged antique ivory buckles for the prize "
T <- strsplit(T, "")
T = sort(unique(tolower(unlist(T))))
T=gsub("[^[:alnum:]]","",T)[-1]
if(sum(T%in%letters)==26){T="pangram"}else{T="not pangram"}
write(as.character(T), stdout())

```



Machine Learning Problem:
```{r}
stop.words <- c("", "a", "also", "an", "and", "are", "as", "at", "be", "but", "by", "for", "from", "had", "has", "have", "he", "his", "i", "if", "in", "is", "it", "its", "not", "of", "on", "or", "reuter", "said", "than", "that", "the", "their", "they", "this", "to", "was", "we", "were", "will", "with", "which", "would")

# Training data
training.input <- readLines("trainingdata.txt")
num.docs <- as.numeric(training.input[1])
training.data <- training.input[2:(num.docs+1)]


doc.id <- vapply(as.list(training.data),
                 function(x) substr(x, start=1, stop=1), "")
doc.text <- vapply(as.list(training.data),
                   function(x) substr(x, start=3, stop=nchar(x)), "")
num.classes <- length(levels(factor(doc.id)))

class.text <- lapply(levels(factor(doc.id)),
                     function(x) paste(doc.text[doc.id==x], collapse=" "))

class.words <- lapply(class.text, function(x) {
    a <- strsplit(x, " ")[[1]]

    # Remove stop words
    a <- a[!(a %in% stop.words)]

    # Use only the most frequent words
    names(head(sort(table(a), decreasing=T), 30))
})

# Test data
test.input <- readLines("stdin")
num.test.docs <- as.numeric(test.input[1])
test.text <- test.input[2:(num.test.docs+1)]
test.words <- lapply(test.text, function(x) unlist(strsplit(x, " ")))

output <- vapply(test.words, function(x) {
    a <- vapply(class.words, function(i) sum(i %in% x), 1)
    which.max(a)
}, 1)
cat(output, sep="\n")
```

```{r}
L<-0
L[[1]] <- "9 6 2015"
L[[2]] <- "6 6 2015"
step1<-strsplit(L[[1]], " ")[,1]
step1<-as.numeric


print(step1)

```


Library Fine problem:
```{r}
# Enter your code here. Read input from STDIN. Print output to STDOUT

L<-0
L[[1]] <- "9 6 2015"
L[[2]] <- "6 6 2015"

actual1 <- sapply(strsplit(L[[1]], " "), as.numeric)

actual2<-actual1[,1]

names(actual) <- c("day", "month", "year")


expected <- sapply(strsplit(L[[2]], " "), as.numeric)[,1]
names(expected) <- c("day","month","year")

days.late <- (actual["year"] - expected["year"]) * 365 +
  (actual["month"] - expected["month"]) * 12 +
  (actual["day"] - expected["day"])

fine <- 0
if (days.late < 0) {
    fine <- 0
} else if ((actual["month"] == expected["month"]) &&
          (actual["year"] == expected["year"])) {
    fine <- 15 * days.late   
} else if (actual["year"] == expected["year"]) {
    fine <- (actual["month"] - expected["month"]) * 500
} else {
    fine <- 10000
}
cat(fine)
```



Challenge 5: Plus Minus
```{r}
# build test cast
X<-as.numeric(c(-4, 3, -9,  0,  4 , 1))


#Start code here
data=suppressWarnings(readLines(file("stdin")))
data=strsplit(data,split=" ")
N=as.numeric(data[[1]])
X=as.numeric(data[[-1]])

Pos<-(X>0)
Neg<-(X<0)              
Zero<-(X==0)

out=as.matrix(1:3, nrows = 3, ncols=1)
out[1,1]<-length(which(Pos == TRUE))/length(Pos)
out[2,1]<-length(which(Neg == TRUE))/length(Neg)
out[3,1]<-length(which(Zero == TRUE))/length(Zero)

#end code
write(as.character(out), stdout())
```

Challenge 4: Simple Array Sum
```{r}

# build test cast
r1<-c(11, 2, 4)
r2<-c(4,5,6)
r3<-c(10, 8, -12)
mydata <- rbind(r1, r2, r3)
NxN<-as.matrix(nrows = 3, ncols = 3, mydata)

#start code here....check that output comes in legit
data=suppressWarnings(readLines(file("stdin")))
data=strsplit(data,split=" ")
N=as.numeric(data[[1]])
NxN=as.numeric(data[[-1]])

#cut to the test case data....
diag1=as.numeric(0)
diag2=as.numeric(0)
for(i in 1:N){
        diag1=as.numeric(NxN[[i+1]][i])+as.numeric(diag1)}

for(i in N:1){
        diag2=as.numeric(NxN[[n-i+2]][i])+as.numeric(diag2)}

out<-sum(D1)-sum(diag(NxN))


#end code
write(as.character(out), stdout())
```


Challenge 3: A very big sum
```{r}
stdin <- scan("/dev/stdin")
out <- sum(stdin[-1])
write(as.character(out), stdout())

```


Challenge #2: Gold
```{r}

T <- suppressWarnings(readLines(file("stdin")))
T <- strsplit(T, " ")

Ti <- as.numeric(T[[1]])
Tnew <- T[-1]
for(i in 1:Ti){
    out <- sum(as.numeric(Tnew[[i]]))
    write(as.character(out), stdout())
    
}
```

Challenge #1 (gold)
```{r}

#remember that STDIN and STOUT are not actual variables...they are more like locations
# read the input file as given by HackerRank
nums <- read.table("/dev/stdin", sep=" ");

OR 

#use case tester....need to be able to include 
nums<- matrix(nrow = 2, ncol =4)
nums[1,1:4]<-c(1, 2, 3, 44)
nums[2,1:3]<-c(10, 20, 30)

write.table(nums, sep = " ", append=T, row.names = F, col.names = F)

#transpose the data from side by side to top to bottom
nums2 <- as.list(as.data.frame(t(nums)))

#convert the new data frame to numeric
nums3<-as.numeric(nums2)

#add the elements of the data frame
xx<-sum(nums3)

#print the data frame, eliminating any names, etc
write.table(xx, sep = "", append=T, row.names = F, col.names = F)

```




